---
title: "Mortality Impact of NRP vs DPP Heart Procurement Techniques - Analysis"
author: "Julia Ran, Anji Wall, Nikhil Narang, Kiran Khush, Jordan Hoffman, Will Parker"
date: "03/22/2023"
output:
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
    number_sections: yes
  html_notebook:
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 6, fig.height = 4.5, fig.align = "right")
```

```{=tex}
\setlength{\parskip}{6pt}
\newpage
```

#Load libraries
```{r load package}
library(tidyverse)
library(caret)
library(haven)
library(rmdformats)
library(ggpubr)
library(here)
library(readr)
library(lubridate)
library(survival)
library(AER)
library(stargazer)
library(survminer)
library(rms)
library(tab)
library(kableExtra)
library(broom)
library(finalfit)
library(gtsummary)
library(ggsci)
library(labelled)
library(rpart)
library(ppsr)
library(janitor)
library(data.table)
library(ggplot2)
library(PSweight)
library(stats)
library(segmented)
library(timereg)
library(MatchIt)
library(cobalt)
library(jtools)
library(splitstackshape)
library(survey)
library("sf")
library(tidyverse)
library(censusapi)
library(tidyselect)
library(tidyr)
library(ggplot2)
library(maps)
library(coxme)
library(cowplot)
library(gridExtra)
library(extrafont)
library(survRM2)
library(tableone)
```
# Set color scheme
```{r color scheme}
custom_colors <- c(
  `red` = "#A33E3E",
  `blue` = "#7CA5CB",
  `green` = "#7EA16B",
  `orange` = "#E18335",
  `grey` = "#5A5A5A"
  )

custom_col <- function(...) {
  cols <- c(...)

  if (is.null(cols))
    return (drsimonj_colors)

  custom_colors[cols]
}

custom_palettes <- list(
  `main`  = custom_col("green","blue", "red"),
  `dbd_dcd` = custom_col("green", "orange"),
  `dpp_nrp` = custom_col("blue", "red"),
  `quartiles` = custom_col("blue", "green", "grey", "orange", "red")
)


custom_pal <- function(palette = "main", reverse = FALSE, ...) {
  pal <- custom_palettes[[palette]]

  if (reverse) pal <- rev(pal)

  colorRampPalette(pal, ...)
}

scale_color_main <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("colour", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

scale_color_dbd <- function(palette = "dbd_dcd", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("colour", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

scale_color_nrp <- function(palette = "nrp_srr", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("colour", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}


scale_color_quartile <- function(palette = "quartiles", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("colour", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
scale_fill_main <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

scale_fill_dbd <- function(palette = "dbd_dcd", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

scale_fill_nrp <- function(palette = "nrp_srr", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
```
# Set KM curve themes
```{r}
#set graph themes
theme_unmatched <- theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12, hjust = 0.5),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank(),
                   legend.title = element_blank()
                   )

theme_matched  <- theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_blank(),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12, hjust = 0.5),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
                   )

labels_unmatched <- list(ggtitle("Unmatched Cohorts"))

labels_matched <- list(ggtitle("Propensity Score Matched Cohorts"))
```

# Load data
```{r load data}
#set location of source file
path <- "C:/Users/julia/SRP/S&D/dataset/pubsaf2303/"
load(paste0(path, "clean_data_1113_jhlt.RData"))

center_geocodes <- read.csv(file = "C:/Users/julia/SRP/S&D/dataset/center_geocodes.csv")

#specify study period
study_start <- mdy("01/01/2019")
study_end <- mdy("12/31/2021")

#load font
loadfonts()

#set location for saving output
path_save <- "C:/Users/julia/SRP/S&D/Drafts/Distance/"

#add HCV data to complete_data_dcd
complete_data_dcd <- complete_data_dcd %>% 
  left_join(donor %>% dplyr::select(DONOR_ID, DON_HCV_STAT, DON_HCV_NAT), by = "DONOR_ID") %>% 
  set_variable_labels(DON_HCV_NAT = "Donor HCV NAT Serology") %>% 
  mutate(DON_HCV_NAT = ifelse(DON_HCV_NAT=="P", "Positive", "Negative"))

```

# Figure 1, Histogram of death to cross clamp time
```{r histogram}
#histogram of amount of time between death to cross clamp
hist_clamp <- ggplot(complete_data_dcd, aes(x = death_to_clamp_min, fill = factor(procurement_type)), alpha = 0.7) +
  geom_histogram(binwidth = 1) +
  labs(x = "Death-to-Cross-Clamping Time (Minutes)", y = "Frequency", fill = "Procurement Type") +
  theme_light() +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        text = element_text(size = 8)) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP")) +
  labs(fill = "Procurement Type")

ggsave(paste0(path_save,"Figure1a.tiff"), hist_clamp, dpi = "print",width=7.29, height = 3)

#histogram of withdrawal time
hist_clamp_withdrawal <- ggplot(complete_data_dcd, aes(x = wdt_time_min, fill = factor(procurement_type)), alpha = 0.7) +
  geom_histogram(binwidth = 1) +
  labs(x = "Time from Withdrawal of Life Support to Death (Minutes)", y = "Frequency", fill = "Procurement Type") +
  theme_light() +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        text = element_text(size = 8)) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP")) +
  labs(fill = "Procurement Type") 

ggsave(paste0(path_save,"Figure1b.tiff"), hist_clamp_agonal, dpi = "print",width=7.29, height = 3)

hist_clamp1 <- ggplot(complete_data_dcd, aes(x = death_to_clamp_min, fill = factor(procurement_type)), alpha = 0.7) +
  geom_histogram(binwidth = 1) +
  labs(x = "Death-to-Cross-Clamping Time (Minutes)", y = "Frequency", 
       fill = "Procurement Type",
       title = "A") +
  theme_light() +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE) +
  theme(plot.title = element_text("A"),
        legend.position = "none",
        text = element_text(size = 12, 
                            family = "Calibri Light"))

  

hist_clamp_agonal1 <- ggplot(complete_data_dcd, aes(x = wdt_time_min, fill = factor(procurement_type)), alpha = 0.7) +
  geom_histogram(binwidth = 1) +
  labs(x = "Withdrawal-to-Death Time (Minutes)", y = "Frequency", 
       fill = "Procurement Type",
       title = "B") +
  theme_light() +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        text = element_text(size = 12,
                            family = "Calibri Light")) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP")) +
  labs(fill = "Procurement Type") 

figure1 <- grid.arrange(hist_clamp1, hist_clamp_agonal1, ncol = 1)
ggsave(paste0(path_save,"Figure1_0911.tiff"), figure1, dpi = "print",width=15, height = 10)

```

# Figure 2, Transplant center map by number and procurement type 
```{r figure 2 datasets}
f1_df <- tx_hr %>%
    mutate(list_date = CAN_LISTING_DT, 
           tx_date = REC_TX_DT,
           last_status = TFL_LASTATUS, 
           last_fu_date = TFL_LAFUDATE,
           rec_age = REC_AGE_AT_TX, 
           can_age = CAN_AGE_AT_LISTING,
           REC_CTR_ID) %>% 
  #filter by dates
  filter(tx_date >= mdy("01/01/2019") & tx_date <= study_end) %>% 
  #left_join donor characteristics
  left_join(donor_info, by = c("DONOR_ID", "PX_ID"), suffix = c("_tx", "_d")) %>% 
  mutate(procurement_type = case_when(
    don_dcd == "N"~ "DBD",
    don_dcd == "Y" & death_to_clamp_min >= 50 ~ "DCD_NRP",
    don_dcd == "Y" & death_to_clamp_min < 50 ~ "DCD_DPP"
  )) %>% 
  left_join(donor_geo, by = "DONOR_ID", keep = FALSE, na_matches = "never") %>%
  rename(don_longitude = LONGITUDE,
         don_latitude = LATITUDE) %>% 
  left_join(rec_geo, by = c("REC_CTR_ID" = "TXC_CTR_ID"), keep = FALSE, na_matches = "never") %>% 
  rename(rec_longitude = LONGITUDE,
         rec_latitude = LATITUDE)  %>% 
  filter(complete.cases(PX_ID, tx_date, don_latitude, don_longitude, rec_latitude, rec_longitude, procurement_type)) %>% 
  mutate(month_year = as.yearmon(tx_date)) %>% 
  mutate(distance = mapply(haversine, lat1=don_latitude, long1=don_longitude, lat2=rec_latitude, long2=rec_longitude)) %>% 
  mutate(month_year = as.yearmon(tx_date),
         year = year(tx_date)) 

f2_df <- f1_df %>%
  filter(tx_date >= study_start & tx_date <= study_end) %>% 
  filter(procurement_type != "DBD") %>% 
  group_by(REC_CTR_CD, procurement_type) %>% 
  count()
```

```{r figure 2a}
# Calculate the sum of n for each REC_CTR_CD
sum_by_type <- f1_df %>% 
  filter(tx_date >= study_start, tx_date <= study_end) %>% 
  group_by(REC_CTR_CD) %>% 
  mutate(DCD_DPP = sum(procurement_type == "DCD_DPP"),
         DCD_NRP = sum(procurement_type == "DCD_NRP")) %>% 
 dplyr::select(REC_CTR_CD, DCD_DPP, DCD_NRP, rec_latitude, rec_longitude) %>% 
  distinct() %>% 
  pivot_longer(cols = c(DCD_NRP, DCD_DPP),
               names_to = "procurement_type", values_to = "count") %>% 
  rename(long = rec_longitude, 
         lat = rec_latitude) %>% 
  group_by(procurement_type) %>% 
  arrange(desc(count))

map_data <- map_data("state") %>%dplyr::select(-subregion) 

# New facet label names for supp variable
facet_labels <- c("NRP", "DPP")
names(facet_labels) <- c("DCD_NRP", "DCD_DPP")


procurement_map1 <- ggplot() +
  geom_polygon(data = map_data, aes(x = long, y = lat, group = group), fill = "white", color = "lightgray") +
  xlim(c(-125,-70)) +
  ylim(c(25, 50)) +
  coord_fixed(1.3) +
  geom_point(data = sum_by_type,
             aes(x=long, 
                 y=lat, 
                 size=count, 
                 fill=procurement_type),
             shape = 21,
             alpha = 0.7,
             stroke = NA) +
  theme_light() +
  theme(axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.text = element_blank()) +
  guides(alpha = FALSE, 
         fill = guide_legend(nrow=2,byrow=TRUE),
         color = guide_legend(nrow=2,byrow=TRUE),
         size = guide_legend(override.aes =  list(fill = alpha("grey", 0.7), 
                                                  col = alpha("grey", 0.7)))) +
  scale_size(
      range = c(1, 15),
      guide = guide_legend(
        direction = "horizontal",
        nrow = 2,
      label.position = "bottom",title = "Count")) +
   theme(legend.title = element_blank(),
        legend.text=element_text(size=10,family = "Calibri Light"),
        legend.position = "bottom",
        legend.key.height = unit(3,"mm"),
        legend.key.width = unit(10,"mm"),
        legend.margin = margin(t=0, r=0, b=0, l=0, unit="cm"),
        legend.background = element_blank()
        ) +
  theme(plot.margin=unit(c(0,2,0,2),"mm")) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP"))


ggsave(paste0(path_save,"Figure2a.tiff"), procurement_map1, dpi = "print",width=7.29, height = 5)
```

```{r figure 2b}
# Calculate the sum of n for each REC_CTR_CD
sum_n <- f2_df %>% 
  group_by(REC_CTR_CD) %>% 
  dplyr::summarize(total_n = sum(n))

# Reorder REC_CTR_CD based on total_n
f2_df$REC_CTR_CD <- factor(f2_df$REC_CTR_CD, levels = sum_n$REC_CTR_CD[order(decreasing = TRUE, sum_n$total_n)])

# Create the stacked bar chart with arranged bars
count_by_ctr <- ggplot(f2_df, aes(fill = procurement_type, y = n, x = REC_CTR_CD)) +
  geom_bar(position = "stack", stat = "identity") +
  theme_light() +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.grid = element_blank()) +
  ylab("Number of DCD Transplants") +   
  xlab("Transplant Center") +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP")) +
  scale_color_nrp(palette = "dpp_nrp", discrete = TRUE, guide = "none")+
  labs(fill = "Procurement Type")


ggsave(paste0(path_save,"Figure2b.tiff"), plot = count_by_ctr,height = 7,width = 14,units = "in")

```

```{r combine 2a and 2b}
procurement_map2 <- ggplot() +
  geom_polygon(data = map_data, aes(x = long, y = lat, group = group), fill = "white", color = "lightgray") +
  xlim(c(-125,-70)) +
  ylim(c(25, 50)) +
  coord_fixed(1.3) +
  geom_point(data = sum_by_type,
             aes(x=long, 
                 y=lat, 
                 size=count, 
                 fill=procurement_type),
             shape = 21,
             alpha = 0.7,
             stroke = NA) +
  theme_light() +
  theme(axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.text = element_blank()) +
  guides(alpha = FALSE, 
         fill = FALSE,
         color = FALSE,
         size = guide_legend(override.aes = list(fill = alpha("grey", 0.7),
                             col = alpha("grey", 0.7)),
                             title = "Count")) +
  scale_size(
      range = c(1, 15),
      guide = guide_legend(
        title.hjust = 0,
        label.hjust = 0,
        direction = "horizontal",
        nrow = 2,
      label.position = "right")) +
   theme(legend.title = element_text(size = 12,
                                     family = "Calibri Light"),
        legend.text=element_text(size=10,family = "Calibri Light"),
        legend.position = "right",
        legend.key.height = unit(3,"mm"),
        legend.key.width = unit(3,"mm"),
        legend.background = element_blank(),
        legend.justification = c("right","bottom"),
        legend.text.align = 0,
        legend.title.align = 0,
        ) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE) +
  theme(text = element_text(size = 12, family = "Calibri Light"),
        panel.border = element_blank()) +
  theme(plot.margin=unit(c(0,0,0,0),"cm"),
        plot.title.position = "panel") 

count_by_ctr1 <- ggplot(f2_df, aes(fill = procurement_type, y = n, x = REC_CTR_CD)) +
  geom_bar(position = "stack", stat = "identity") +
  theme_light() +
  ylab("Number of DCD Transplants") +   
  xlab("Transplant Center") +
  guides(fill = guide_legend(title = "Procurement Type",
                             title.hjust = 1,
                             label.hjust = 1)) +
  theme_light()+
  scale_size(
    guide = guide_legend(
        title.hjust = 1,
        label.hjust = 1,
        direction = "horizontal",
        nrow = 2,
      label.position = "right")) +
  scale_fill_nrp(palette = "dpp_nrp", discrete = TRUE, labels= c("DPP", "NRP")) +
  theme(legend.position = c(1,1),
        legend.justification = c("right", "top")) +
  theme(legend.title = element_text(size = 12,
                                     family = "Calibri Light"),
        legend.text=element_text(size=10,family = "Calibri Light"),
        legend.position = c(1,1),
        legend.key.height = unit(3,"mm"),
        legend.key.width = unit(3,"mm"),
        legend.background = element_blank(),
        legend.justification = c("right","top"),
        legend.text.align = 1,
        legend.title.align = 1,
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        text = element_text(size = 12, family = "Calibri Light")
        ) 
  
  
figure2<- grid.arrange(procurement_map2, count_by_ctr1, ncol = 1)

ggsave(paste0(path_save,"Figure2.tiff"), figure2, dpi = "print",width=10, height = 10)

```

# Figure 3, Map of source of organ by procurement type 

```{r figure 3}
data_dcd_non_identical <- f1_df %>% 
  filter(procurement_type != "DBD") %>% 
  filter(rec_longitude != don_longitude & rec_latitude != don_latitude) %>%
  dplyr::select(rec_longitude, rec_latitude, don_longitude, don_latitude, REC_CTR_CD, DON_HOSP_PROV_NUM, procurement_type, distance)

data_dcd_identical <- f1_df %>% 
  filter(procurement_type != "DBD") %>% 
  filter(rec_longitude == don_longitude & rec_latitude == don_latitude) %>% 
  group_by(REC_CTR_CD, DON_HOSP_PROV_NUM, procurement_type) %>% 
  add_count() %>% 
  dplyr::select(rec_longitude, rec_latitude, don_longitude, don_latitude, REC_CTR_CD, DON_HOSP_PROV_NUM, procurement_type, n)


route_by_type <- ggplot() +
  geom_polygon(data = map_data, aes(x = long, y = lat, group = group), fill = "white", color = "lightgray") +
  xlim(c(-125,-70)) +
  ylim(c(25, 50)) +
  coord_fixed(1.3) +
geom_curve(data=data_dcd_non_identical,
             aes(x=don_longitude, y=don_latitude, 
                 xend=rec_longitude, 
                 yend=rec_latitude, 
                 col = procurement_type, alpha = distance),
             size=.5,
             curvature=0.2) +
  geom_point(data=data_dcd_non_identical,
             aes(x=rec_longitude, y=rec_latitude),
                 color = "black",
             size = 1) +
  facet_grid(cols = vars(procurement_type),
             labeller = labeller(.cols = facet_labels)) +
        theme(strip.background = element_rect(fill="grey",
                                        colour="grey",
                                        size = unit(3,"mm")),
              strip.text = element_text(size=10, colour="white",family = "Calibri Light"),              strip.text.x = element_text(margin = margin(b=1,t=1))) +
    theme_light() +
  theme(axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.text = element_blank(),
        legend.position = "bottom") +
  scale_color_main(palette = "dpp_nrp", discrete = TRUE, labels = c("DPP", "NRP")) +
  labs(color = "Procurement Type", alpha = "Distance (NM)") 

ggsave(paste0(path_save,"Figure3_0905.tiff"), route_by_type, dpi = "print",width=7.29, height = 5)
```



# Table 1, Donor and recipient characteristics by procurement type 

```{r table 1}
table1_data <- complete_data_dcd %>% 
  mutate(dpp_nrp = case_when(
    procurement_type == "DCD_DPP" ~ "DPP",
    procurement_type == "DCD_NRP" ~ "NRP"
  ))
  
table1 <- CreateTableOne(data = table1_data,
               vars = c("rec_age_60", 
                        "status",
                         "rec_bilirubin",
                         "rec_dialysis",
                         "rec_sex",
                         "simple_diagnosis",
                         "rec_infection",
                         "treatment",
                         "rec_race_desc",
                         "functional_status",
                         "rec_abo",
                         "rec_bmi",
                         "rec_co",
                         "rec_pcwp",
                         "don_age",
                         "don_sex",
                         "don_bmi",
                         "don_lvef",
                         "don_smoke",
                         "don_abo",
                        "wdt_time_min",
                        "DON_HCV_NAT",
                        "don_angio"),
               factorVars = c("rec_age_60", 
                         "status",
                         "rec_dialysis",
                         "rec_sex",
                         "simple_diagnosis",
                         "treatment",
                         "rec_infection",
                         "rec_race_desc",
                         "functional_status",
                         "rec_abo",
                         "rec_edu",
                         "don_sex",
                         "don_smoke",
                         "don_abo",
                         "DON_HCV_NAT"),
               strata = "dpp_nrp",
              )

table1 <- print(table1, 
      catDigits=1, 
      contDigits=2, 
      pDigits=3, 
      quote=FALSE, 
      missing=FALSE, 
      explain=TRUE, 
      printToggle=TRUE,
      test=TRUE, 
      smd=FALSE, 
      noSpaces=FALSE, 
      padColnames=FALSE, 
      varLabels=TRUE, 
      format=c("fp","f","p","pf")[1], 
      showAllLevels=FALSE, 
      cramVars=NULL, 
      dropEqual=FALSE, 
      exact=c("rec_age_60", 
              "status",
              "rec_dialysis",
              "rec_sex",
              "simple_diagnosis",
              "treatment",
              "rec_race_desc",
              "functional_status",
              "rec_abo",
              "rec_edu",
              "don_sex",
              "don_smoke",
              "don_abo",
              "DON_HCV_NAT"), 
      nonnormal=c("rec_bilirubin",
                  "rec_dialysis",
                  "rec_bmi",
                  "rec_co",
                  "rec_pcwp",
                  "don_age",
                  "don_bmi",
                  "don_lvef",
                  "wdt_time_min"), 
      minMax=FALSE, 
      formatOptions=list(scientific=FALSE))

only_treatments <- table1_data %>% 
  dplyr::select(procurement_type, treatment)

table1_treatment <- CreateTableOne(
  data = only_treatments,
  vars = "treatment",
  factorVars = "treatment",
  strata = "procurement_type"
)

print(table1_treatment, 
      catDigits=1, 
      contDigits=2, 
      pDigits=3, 
      quote=FALSE, 
      missing=FALSE, 
      explain=TRUE, 
      printToggle=TRUE,
      test=TRUE, 
      smd=FALSE, 
      noSpaces=FALSE, 
      padColnames=FALSE, 
      varLabels=TRUE, 
      format=c("fp","f","p","pf")[1], 
      showAllLevels=FALSE, 
      cramVars=NULL, 
      dropEqual=FALSE, 
      exact=NULL)

write.csv(table1, file = paste0(path_save, "table1_1103.csv"))
```

# Survival Analysis
```{r}
#make agonal time and bmi into bins
complete_data_dcd <- complete_data_dcd %>% 
  mutate(wdt_time_qtile = ntile(wdt_time_min,4)) %>%
  mutate(wdt_time_qtile = factor(wdt_time_qtile, levels = c("1", "2", "3", "4"),labels = c("1st quartile", "2nd quartile", "3rd quartile", "4th quartile"))) %>%   mutate(don_bmi_qtile = ntile(don_bmi, 4)) %>% 
  mutate(don_bmi_qtile = factor(don_bmi_qtile, levels = c("1", "2", "3", "4"),labels = c("1st quartile", "2nd quartile", "3rd quartile", "4th quartile")))

#pre-match matchit object
data_nrp_dpp <- complete_data_dcd %>% 
  mutate(nrp = ifelse(procurement_type== "DCD_NRP", 1, 0))
```

## Unadjusted Kaplan-Meier Curve
```{r 365}
# Fit Kaplan-Meier survival curves for each group
fit <- survfit(Surv(surv_time_365, dead_1y) ~ procurement_type, data = complete_data_dcd)

grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
}

km_plot <- ggsurvplot(fit, data = complete_data_dcd, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", 
           ylab = "Survival Probability",
           title = "Unmatched Cohorts (n=318)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 

km_plot_no_ci <- ggsurvplot(fit, data = complete_data_dcd, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = FALSE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Time", 
           ylab = "Survival Probability",
           title = "Unmatched cohorts (n=318)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 


```

```{r 547}
# Fit Kaplan-Meier survival curves for each group
fit_18m <- survfit(Surv(surv_time_18m, dead_18m) ~ procurement_type, data = complete_data_dcd)

grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
}

km_plot_18m <- ggsurvplot(fit_18m, data = complete_data_dcd, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", ylab = "Survival Probability",
           title = "Unmatched Cohorts (n=318)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 

km_plot_no_ci_18m <- ggsurvplot(fit_18m, data = complete_data_dcd, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = FALSE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", ylab = "Survival Probability",
           title = "Unmatched Cohorts (n=318)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 

#compare survival between procurement groups
survdiff(Surv(surv_time_18m, dead_18m) ~ procurement_type, data = complete_data_dcd)

```

## 1:1 Propensity Score Match
```{r}
bal.tab(procurement_type ~ agonal_time_bin +
                   rec_age_60 +
                   status +
                   rec_bilirubin +
                   rec_dialysis +
                   rec_sex +
                   simple_diagnosis +
                   rec_infection +
                   treatment +
                   rec_race_desc +
                   tMCS +
                   vad +
                   functional_status +
                   rec_abo +
                   rec_bmi +
                   rec_co +
                   rec_pcwp +
                   don_age +
                   don_sex +
                   don_bmi +
                   don_lvef +
                   don_abo,  
                    data = data_nrp_dpp,
        estimand = "ATT",
        thresholds = c(m = 0.1)
)


#1:1 OLS PS matching without replacement
post_match_nrp_dpp <- matchit(nrp ~ 
                                wdt_time_qtile +
                                rec_age_60 +
                                treatment +
                                don_age +
                                don_bmi,
                   data = data_nrp_dpp,method = "optimal",
                   distance = "glm",
                   link = "logit",
                   estimand = "ATT",
                   replace = FALSE,
                   caliper = 0.2)


bal.tab(post_match_nrp_dpp, stats = c("m", "v"), thresholds = c(m = .1))

#visualize the distribution of propensity scores of those who were matched
plot(post_match_nrp_dpp, type = "jitter", interactive = FALSE)

#visualize balance
plot(post_match_nrp_dpp, type = "density", interactive = FALSE, 
     which.xs = ~ don_bmi_qtile + agonal_time_bin)


new.names <- c(`wdt_time_qtile_1st quartile` = "Withdrawal-to-Death Time: 1st Quartile",
               treatment_ECMO = "Recipient Treatment: ECMO",
               `treatment_High-dose Inotropes` = "Recipient Treatment: High-dose Inotropes",
               treatment_None = "Recipient Treatment: None",
               `rec_age_60_Over 60` = "Recipient Age: Over 60",
               `wdt_time_qtile_2nd quartile` = "Withdrawal-to-Death Time: 2nd Quartile",
               `treatment_IABP` = "Recipient Treatment: IABP",
               `wdt_time_qtile_3rd quartile` = "Withdrawal-to-Death Time: 3rd Quartile",
               treatment_Exception = "Recipient Treatment: Exception",
               `treatment_Other MCS` = "Recipient Treatment: Other MCS",
               `don_age` = "Donor Age (Years)",
               `treatment_Low-dose Inotropes` = "Recipient Treatment: Low-dose Inotropes",
               `wdt_time_qtile_4th quartile` = "Withdrawal-to-Death Time: 4th Quartile",
               treatment_LVAD = "Recipient Treatment: LVAD",
               `don_bmi` = "Donor BMI")

love_plot_nrp_dpp <- love.plot(post_match_nrp_dpp, 
          drop.distance = TRUE, 
          stars = "raw",
          var.order = "adjusted",
          var.names = new.names,
          abs = TRUE,
          line = TRUE, 
          thresholds = c(m = .1),
          colors = c("#A33E3E", "#7CA5CB")) +
  theme_light() +
  theme(legend.position = c(.75, .3),
        legend.box.background = element_rect(), 
        legend.box.margin = margin(1, 1, 1, 1),
        axis.text.y = element_text(size = 10),
        panel.grid = element_blank())


ggsave(paste0(path_save,"Supplemental Figure 1.tiff"), plot = love_plot_nrp_dpp,height = 7,width = 14,units = "in")


#get matched data
matched_nrp_dpp <- match.data(post_match_nrp_dpp, group = "all",distance = "prop_score", data = data_nrp_dpp, drop.unmatched = TRUE)

#summarize
View(matched_nrp_dpp %>% group_by(nrp) %>% count())
```

```{r}
# Fit Kaplan-Meier survival curves for each group
fit_matched <- survfit(Surv(surv_time_365, dead_1y) ~ procurement_type, data = matched_nrp_dpp)

grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
}

km_plot_matched <- ggsurvplot(fit_matched, data = matched_nrp_dpp, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", 
           ylab = "Survival Probability",
           title = "Matched Cohorts (n=204)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 


#make graphs with CI
dcd_graph <- list()
dcd_graph[[1]] <- km_plot
dcd_graph[[2]] <- km_plot_matched
dcd_graph <- arrange_ggsurvplots(dcd_graph, print = TRUE,
  ncol = 2, nrow = 1, risk.table.height = 0.2)

ggsave(paste0(path_save, "Figure 4 0114.tiff"),dcd_graph, dpi = "print",width=7.29, height = 5)
```

# Table S1: Donor and recipient characteristics by procurement type for matched cohorts
```{r table s1}
tables1_data <- matched_nrp_dpp %>% 
  mutate(dpp_nrp = case_when(
    procurement_type == "DCD_DPP" ~ "DPP",
    procurement_type == "DCD_NRP" ~ "NRP"
  ))
  
tables1 <- CreateTableOne(data = tables1_data,
               vars = c("rec_age_60", 
                        "status",
                         "rec_bilirubin",
                         "rec_dialysis",
                         "rec_sex",
                         "simple_diagnosis",
                         "rec_infection",
                         "treatment",
                         "rec_race_desc",
                         "functional_status",
                         "rec_abo",
                         "rec_bmi",
                         "rec_co",
                         "rec_pcwp",
                         "don_age",
                         "don_sex",
                         "don_bmi",
                         "don_lvef",
                         "don_smoke",
                         "don_abo",
                        "wdt_time_min",
                        "DON_HCV_NAT",
                        "don_angio"),
               factorVars = c("rec_age_60", 
                         "status",
                         "rec_dialysis",
                         "rec_sex",
                         "rec_infection",
                         "simple_diagnosis",
                         "treatment",
                         "rec_race_desc",
                         "functional_status",
                         "rec_abo",
                         "rec_edu",
                         "don_sex",
                         "don_smoke",
                         "don_abo",
                         "DON_HCV_NAT"),
               strata = "procurement_type",
              )

tables1 <- print(tables1, 
      catDigits=1, 
      contDigits=2, 
      pDigits=3, 
      quote=FALSE, 
      missing=FALSE, 
      explain=TRUE, 
      printToggle=TRUE,
      test=TRUE, 
      smd=FALSE, 
      noSpaces=FALSE, 
      padColnames=FALSE, 
      varLabels=TRUE, 
      format=c("fp","f","p","pf")[1], 
      showAllLevels=FALSE, 
      cramVars=NULL, 
      dropEqual=FALSE, 
      exact=c("rec_age_60", 
              "status",
              "rec_dialysis",
              "rec_sex",
              "simple_diagnosis",
              "treatment",
              "rec_race_desc",
              "functional_status",
              "rec_abo",
              "rec_edu",
              "don_sex",
              "don_smoke",
              "don_abo",
              "DON_HCV_NAT"), 
      nonnormal=c("rec_bilirubin",
                  "rec_dialysis",
                  "rec_bmi",
                  "rec_co",
                  "rec_pcwp",
                  "don_age",
                  "don_bmi",
                  "don_lvef",
                  "wdt_time_min"), 
      minMax=FALSE, 
      formatOptions=list(scientific=FALSE))

write.csv(tables1, file = paste0(path_save, "table_s1_1028.csv"))
```




## Kaplan-Meier Curve after Propensity Score Matching
```{r 365 after match}
# Fit Kaplan-Meier survival curves for each group
fit_matched_dcd <- survfit(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp_all)

fit_dcd <- survfit(Surv(surv_time_365, dead_1y) ~ nrp, data = data_nrp_dpp)

#adjust grid structure
grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
}

#pre-match KM with CI
km_dcd_plot <- ggsurvplot(fit_dcd, data = data_nrp_dpp, risk.table = TRUE, 
           legend.labs = c("DPP", "NRP"),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           ylim = c(0.80, 1.0),
           xlim = c(0,365),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           ggtheme = theme_unmatched) +
  labels_unmatched

ggsave(paste0(path_save, "km_dcd_plot_0905.tiff"),km_dcd_plot, dpi = "print",width=7.29, height = 5)


#matched KM
km_dcd_matched <- ggsurvplot(fit_matched_dcd, data = matched_nrp_dpp, risk.table = TRUE, 
           legend.labs = c("DPP","NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           ylim = c(0.80, 1.0),
           xlim = c(0,365),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           ggtheme = theme_matched
) +
  labels_matched

ggsave(paste0(path_save, "km_dcd_matched_0905.tiff"),km_dcd_matched, dpi = "print",width=7.29, height = 5)


#proportion test
prop.test(x = c(102-9,102-7), n = c(102,102))
#compare survival between procurement groups
#post-match
survdiff(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp_all)
#pre-match
survdiff(Surv(surv_time_365, dead_1y) ~ nrp, data = data_nrp_dpp)

#make graphs with CI
dcd_with_ci <- list()
dcd_with_ci[[1]] <- km_dcd_plot
dcd_with_ci[[2]] <- km_dcd_matched 
dcd_with_ci <- arrange_ggsurvplots(dcd_with_ci, print = TRUE,
  ncol = 2, nrow = 1, risk.table.height = 0.2)

ggsave(paste0(path_save, "Figure4_w_CI_1016.tiff"),dcd_with_ci, dpi = "print",width=7.29, height = 5)
```

```{r 547 after match}
# Fit Kaplan-Meier survival curves for each group
fit_matched_dcd_18m <- survfit(Surv(surv_time_18m, dead_18m) ~ nrp, data = matched_nrp_dpp)

fit_dcd_18m <- survfit(Surv(surv_time_18m, dead_18m) ~ nrp, data = data_nrp_dpp)

#adjust grid structure
grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
}

#pre-match KM with CI
km_dcd_plot_18m <- ggsurvplot(fit_dcd_18m, data = data_nrp_dpp, risk.table = TRUE, 
           legend.labs = c("DPP", "NRP"),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", ylab = "Survival Probability",
           ylim = c(0.70, 1.0),
           xlim = c(0,547),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           ggtheme = theme_unmatched,
           tables.y.text = FALSE,
           tables.theme = theme_cleantable(),
           title = "Unmatched Cohorts")

ggsave(paste0(path_save, "km_dcd_plot_1016.tiff"),km_dcd_plot_18m, dpi = "print",width=7.29, height = 5)


#matched KM
km_dcd_matched_18m <- ggsurvplot(fit_matched_dcd_18m, data = matched_nrp_dpp, risk.table = TRUE,
           legend.labs = c("DPP","NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", ylab = "Survival Probability",

           ylim = c(0.70, 1.0),
           xlim = c(0,547),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           ggtheme = theme_matched,
           tables.y.text = FALSE,
           tables.theme = theme_cleantable(),
           title = "Propensity Score Matched Cohorts") 


ggsave(paste0(path_save, "km_dcd_matched_1016.tiff"),km_dcd_matched_18m, dpi = "print",width=7.29, height = 5)


#proportion test
prop.test(x = c(102-9,102-7), n = c(102,102))
#compare survival between procurement groups
#post-match
survdiff(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp)
#pre-match
survdiff(Surv(surv_time_365, dead_1y) ~ nrp, data = data_nrp_dpp)

#make graphs with CI
dcd_with_ci_18m <- list()
dcd_with_ci_18m[[1]] <- km_dcd_plot_18m
dcd_with_ci_18m[[2]] <- km_dcd_matched_18m
dcd_with_ci_18m <- arrange_ggsurvplots(dcd_with_ci_18m, print = TRUE,
  ncol = 2, nrow = 1, risk.table.height = 0.2)

ggsave(paste0(path_save, "Figure4_w_CI_18m.tiff"),dcd_with_ci_18m, dpi = "print",width=7.29, height = 5)
```

# Estimate Cox-Proportional Hazard Fixed Effect Model
## Table 2, Cox-Proportional Hazard Model Output
```{r 365 table 2 }
fit_cox_matched <- coxph(Surv(surv_time_365, dead_1y) ~
                      nrp,
                    data = matched_nrp_dpp, cluster = subclass)

summary(fit_cox_matched)
cox.zph(fit_cox_matched)

fit_cox_unmatched <- coxph(Surv(surv_time_365, dead_1y) ~
                      nrp,
                    data = data_nrp_dpp)

cox.zph(fit_cox_unmatched)

summary(fit_cox_unmatched)

export_summs(fit_cox_unmatched,
     fit_cox_matched, 
     scale = TRUE,
     model.names = c("Unmatched", "PS Matched"),
     coefs = c("Procurement Type NRP" = "nrp"),
     number_format = "%.2f",
     statistics = c(N = "n", "N Events" = "nevent"),
     align = ".",
     error_format = "({conf.low} to {conf.high})",
     to.file = "xlsx",
     file.name = paste0(path_save,"Table2_1.xlsx"))
                             
```

```{r 547 table 2}
fit_cox_matched_18m <- coxph(Surv(surv_time_18m, dead_18m) ~
                      nrp,
                    data = matched_nrp_dpp)

summary(fit_cox_matched_18m)

fit_cox_unmatched_18m <- coxph(Surv(surv_time_18m, dead_18m) ~
                      nrp,
                    data = data_nrp_dpp)

summary(fit_cox_unmatched_18m)

export_summs(fit_cox_unmatched,
     fit_cox_matched, 
     scale = TRUE,
     model.names = c("Unmatched", "PS Matched"),
     coefs = c("Procurement Type NRP" = "nrp"),
     number_format = "%.2f",
     statistics = c(N = "n", "N Events" = "nevent"),
     align = ".",
     error_format = "({conf.low} to {conf.high})",
     to.file = "xlsx",
     file.name = paste0(path_save,"Table2_1.xlsx"))
                             
```

# Estimate Mixed Effect Model
## COXME model
```{r 365 coxme}

fit_coxme_matched <- coxme(Surv(surv_time_365, dead_1y) ~
                      nrp + (1|REC_CTR_CD),
                    data = matched_nrp_dpp)

summary(fit_coxme_matched)

fit_coxme_unmatched_full <- coxme(Surv(surv_time_365, dead_1y) ~
                      nrp + wdt_time_qtile + rec_age_60 + treatment + don_age + don_bmi + (1|REC_CTR_CD),
                    data = data_nrp_dpp)

data_nrp_dpp$treatment <- relevel(as.factor(data_nrp_dpp$treatment), ref = "LVAD")
fit_coxme_unmatched_empty <- coxme(Surv(surv_time_365, dead_1y) ~
                      nrp + (1|REC_CTR_CD),
                    data = data_nrp_dpp)

fit_coxme_unmatched_empty
fit_coxme_unmatched_full

```

```{r 547 coxme}

fit_coxme_matched_18m <- coxme(Surv(surv_time_18m, dead_18m) ~
                      nrp + (1|REC_CTR_CD),
                    data = matched_nrp_dpp)


fit_coxme_unmatched_full <- coxme(Surv(surv_time_18m, dead_18m) ~
                      nrp + wdt_time_qtile + rec_age_60 + treatment + don_age + don_bmi + (1|REC_CTR_CD),
                    data = data_nrp_dpp)

data_nrp_dpp$treatment <- relevel(as.factor(data_nrp_dpp$treatment), ref = "LVAD")
fit_coxme_unmatched_empty <- coxme(Surv(surv_time_18m, dead_18m) ~
                      nrp + (1|REC_CTR_CD),
                    data = data_nrp_dpp)

summary(fit_coxme_matched_18m)
fit_coxme_unmatched_empty
fit_coxme_unmatched_full

```

## Split matched data
```{r split matched data}
matched_nrp <- matched_nrp_dpp %>% filter(nrp ==1) %>% dplyr::select(surv_time_365, dead_1y, REC_CTR_CD)

matched_dpp <- matched_nrp_dpp %>% filter(nrp==0) %>% dplyr::select(surv_time_365, dead_1y, REC_CTR_CD)
```

## NRP variation
```{r nrp variations}
#NRP only, matched data
model_nrp <- coxph(Surv(surv_time_365,dead_1y) ~ frailty(REC_CTR_CD,distribution="gaussian"),
  data=matched_nrp)

frailty_nrp <- model_nrp$history[[1]]$theta

sf_nrp <- survfit(model_nrp)

surv.time_nrp <- sf_nrp$time
H0_nrp <- sf_nrp$cumhaz

h0_nrp <- c(H0_nrp[1],diff(H0_nrp))

frailty_nrp1 <- model_nrp$frail
frailty.summary_nrp <- quantile(frailty_nrp1)

h.min_nrp <- h0_nrp*exp(-2*sqrt(frailty_nrp))
h.q1_nrp <- h0_nrp*exp(-sqrt(frailty_nrp))
h.q3_nrp <- h0_nrp*exp(sqrt(frailty_nrp))
h.max_nrp <- h0_nrp*exp(2*sqrt(frailty_nrp))

H.min_nrp <- cumsum(h.min_nrp)
H.q1_nrp <- cumsum(h.q1_nrp)
H.q3_nrp <- cumsum(h.q3_nrp)
H.max_nrp <- cumsum(h.max_nrp)

S0_nrp <- exp(-H0_nrp)
S.min_nrp <- exp(-H.min_nrp)
S.q1_nrp <- exp(-H.q1_nrp)
S.q3_nrp <- exp(-H.q3_nrp)
S.max_nrp <- exp(-H.max_nrp)
```

## DPP variation
```{r dpp variations}
#dpp
model_dpp <- coxph(Surv(surv_time_365,dead_1y) ~ frailty(REC_CTR_CD,distribution="gaussian"),
  data=matched_dpp)

frailty_dpp <- model_dpp$history[[1]]$theta

sf_dpp <- survfit(model_dpp)

surv.time_dpp <- sf_dpp$time
H0_dpp <- sf_dpp$cumhaz

h0_dpp <- c(H0_dpp[1],diff(H0_dpp))

frailty_dpp1 <- model_dpp$frail
frailty.summary <- quantile(frailty_dpp)

h.min_dpp <- h0_dpp*exp(-2*sqrt(frailty_dpp))
h.q1_dpp <- h0_dpp*exp(-sqrt(frailty_dpp))
h.q3_dpp <- h0_dpp*exp(sqrt(frailty_dpp))
h.max_dpp <- h0_dpp*exp(2*sqrt(frailty_dpp))

H.min_dpp <- cumsum(h.min_dpp)
H.q1_dpp <- cumsum(h.q1_dpp)
H.q3_dpp <- cumsum(h.q3_dpp)
H.max_dpp <- cumsum(h.max_dpp)

S0_dpp <- exp(-H0_dpp)
S.min_dpp <- exp(-H.min_dpp)
S.q1_dpp <- exp(-H.q1_dpp)
S.q3_dpp <- exp(-H.q3_dpp)
S.max_dpp <- exp(-H.max_dpp)

# Create the data frames for DPP and NRP
dpp_data <- data.frame(
  time = surv.time_dpp,
  max = S.max_dpp,
  q3 = S.q3_dpp,
  avg = S0_dpp,
  q1 = S.q1_dpp,
  min = S.min_dpp) %>% 
  mutate(procurement_type = "DPP")

nrp_data <- data.frame(
  time = surv.time_nrp,
  max = S.max_nrp,
  q3 = S.q3_nrp,
  avg = S0_nrp,
  q1 = S.q1_nrp,
  min = S.min_nrp) %>% 
  mutate(procurement_type = "NRP")

#bind two datasets
combined_data <- rbind(dpp_data, nrp_data)

```

## Figure 5. 
```{r variation graphs}
# Wrap the legend labels into two lines
legend_labels <- as.factor(c(
  "Hazard 2 SD above mean",
  "Hazard 1 SD above mean",
  "Average transplant center",
  "Hazard 1 SD below mean",
  "Hazard 2 SD below mean"
))
wrapped_labels <- str_wrap(legend_labels, width = 10)

# Create the base plot
base_plot <- ggplot(combined_data, aes(x = time)) +
  geom_line(aes(y = max, color = wrapped_labels[1])) +
  geom_line(aes(y = q3, color = wrapped_labels[2]), linetype = "dashed") +
  geom_line(aes(y = avg, color = wrapped_labels[3]), linetype = "dotted") +
  geom_line(aes(y = q1, color = wrapped_labels[4]), linetype = "dotdash") +
  geom_line(aes(y = min, color = wrapped_labels[5]), linetype = "longdash") +
  theme_light() +
  scale_color_manual(values = c("#7CA5CB","#7EA16B","#5A5A5A","#E18335","#A33E3E"),breaks = wrapped_labels) +
  ylim(0.88, 1.00)
 
# Create side-by-side plots using facet_grid
combined_plot <- base_plot +
  facet_grid(. ~ procurement_type, scales = "free_x", space = "free_x") +
        theme(strip.background = element_rect(fill="grey",
                                        colour="grey",
                                        size = unit(3,"mm")),
              strip.text = element_text(size=10, colour="white",family = "Calibri Light"),              strip.text.x = element_text(margin = margin(b=1,t=1))) +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 8),
    legend.key.width = unit(2, "lines"),
    legend.title = element_blank()
  ) +
  labs(
    x = "Time",
    y = "Survival Probability" # Updated Y-axis title
    )


#print graph
ggsave(paste0(path_save,"Figure5_0905.tiff"), plot = combined_plot,height = 3,width = 7.29,units = "in")

```

# Estimate restricted mean survival time
```{r}
survdata_unmatched <- data_nrp_dpp %>% 
  dplyr::select(nrp,
         surv_time_365,
         dead_1y) 

unmatched_surv_time <- as.numeric(survdata_unmatched$surv_time_365)
unmatched_dead_1y <- as.numeric(survdata_unmatched$dead_1y)
unmatched_nrp <- as.numeric(survdata_unmatched$nrp)

mean_survival_unmatched<- rmst2(unmatched_surv_time, unmatched_dead_1y,unmatched_nrp)


survdata_matched <- matched_nrp_dpp_all%>% 
  dplyr::select(nrp,
         surv_time_365,
         dead_1y) 

matched_surv_time <- as.numeric(survdata_matched$surv_time_365)
matched_dead_1y <- as.numeric(survdata_matched$dead_1y)
matched_nrp <- as.numeric(survdata_matched$nrp)

mean_survival_matched<- rmst2(matched_surv_time, matched_dead_1y,matched_nrp)

mean_survival_matched
mean_survival_unmatched
```

```{r}
#distribution of agonal time
nrp_agonal <- complete_data_dcd %>% filter(procurement_type=="DCD_NRP") %>% dplyr::select(agonal_time_min) %>% unlist()

dpp_agonal <- complete_data_dcd %>% filter(procurement_type=="DCD_DPP") %>% dplyr::select(agonal_time_min) %>% unlist()

t.test(nrp_agonal, dpp_agonal)

max(nrp_agonal)
dpp_data
```

# Sensitivity Analysis
## Adding distance
```{r}
data_nrp_dpp <- data_nrp_dpp %>% 
  mutate(distance_qtile = ntile(distance,4)) %>% 
  mutate(distance_qtile = factor(distance_qtile, levels = c("1", "2", "3", "4"),labels = c("1st quartile", "2nd quartile", "3rd quartile", "4th quartile")))

#add distance
post_match_nrp_dpp_distance <- matchit(nrp ~ 
                                wdt_time_qtile +
                                rec_age_60 +
                                treatment +
                                don_age +
                                don_bmi +
                                distance,
                   data = data_nrp_dpp,method = "optimal",
                   distance = "glm",
                   link = "logit",
                   estimand = "ATT",
                   replace = FALSE)

new.names <- c(treatment_ECMO = "Recipient Treatment: ECMO",
               `treatment_High-dose Inotropes` = "Recipient Treatment: High-dose Inotropes",
               treatment_None = "Recipient Treatment: None",
               `rec_age_60_Over 60` = "Recipient Age: Over 60",
               `treatment_IABP` = "Recipient Treatment: IABP",
               treatment_Exception = "Recipient Treatment: Exception",
               don_angio_Performed = "Donor Coronary Angiogram: Performed",
               `treatment_Other MCS` = "Recipient Treatment: Other MCS",
               `don_age` = "Donor Age (Years)",
               `treatment_Low-dose Inotropes` = "Recipient Treatment: Low-dose Inotropes",
               `wdt_time_qtile_1st quartile` = "Withdrawal-to-Death Time: 1st Quartile",
               `wdt_time_qtile_2nd quartile` = "Withdrawal-to-Death Time: 2nd Quartile",
               `wdt_time_qtile_3rd quartile` = "Withdrawal-to-Death Time: 3rd Quartile",
               `wdt_time_qtile_4th quartile` = "Withdrawal-to-Death Time: 4th Quartile",
               treatment_LVAD = "Recipient Treatment: LVAD",
               distance = "Donor-Recipient Distance",
               # `distance_qtile_1st quartile` = "Distance: 1st Quartile",
               # `distance_qtile_2nd quartile` = "Distance: 2nd Quartile",
               # `distance_qtile_3rd quartile` = "Distance: 3rd Quartile",
               # `distance_qtile_4th quartile` = "Distance: 4th Quartile",
               don_bmi = "Donor BMI")

love_plot_with_distance <- love.plot(post_match_nrp_dpp_distance, 
          drop.distance = TRUE, 
          stars = "raw",
          var.order = "adjusted",
          var.names = new.names,
          abs = TRUE,
          line = TRUE, 
          thresholds = c(m = .1),
          colors = c("#A33E3E", "#7CA5CB")) +
  theme_light() +
  theme(legend.position = c(.75, .3),
        legend.box.background = element_rect(), 
        legend.box.margin = margin(1, 1, 1, 1),
        axis.text.y = element_text(size = 10),
        panel.grid = element_blank())

#get matched data
matched_nrp_dpp_distance <- match.data(post_match_nrp_dpp_distance, group = "all",distance = "prop_score", data = data_nrp_dpp, drop.unmatched = TRUE)

fit_matched_dcd_distance <- survfit(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp_distance)

#matched KM
matched_with_distance <- ggsurvplot(fit_matched_dcd_distance, data = matched_nrp_dpp_distance, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", 
           ylab = "Survival Probability",
           title = "Kaplan-Meier Survival Curve",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 

ggsave(paste0(path_save,"Supplemental Figure S2_1.tiff"), plot = love_plot_with_distance,height = 7,width = 14,units = "in")
ggsave(paste0(path_save, "Supplemental Figure S3_1.tiff"), plot = matched_with_distance, dpi = "print",width=7.29, height = 5)

```

## Adding functional status
```{r}
post_match_nrp_dpp_fs <- matchit(nrp ~ 
                                wdt_time_qtile +
                                rec_age_60 +
                                treatment +
                                don_age +
                                don_bmi +
                                functional_status,
                   data = data_nrp_dpp,method = "optimal",
                   distance = "glm",
                   link = "logit",
                   estimand = "ATT",
                   replace = FALSE)

new.names <- c(
               treatment_ECMO = "Recipient Treatment: ECMO",
               `treatment_High-dose Inotropes` = "Recipient Treatment: High-dose Inotropes",
               treatment_None = "Recipient Treatment: None",
               `rec_age_60_Over 60` = "Recipient Age: Over 60",
               `treatment_IABP` = "Recipient Treatment: IABP",
               treatment_Exception = "Recipient Treatment: Exception",
               don_angio_Performed = "Donor Coronary Angiogram: Performed",
               `treatment_Other MCS` = "Recipient Treatment: Other MCS",
               `don_age` = "Donor Age (Years)",
               `treatment_Low-dose Inotropes` = "Recipient Treatment: Low-dose Inotropes",
               treatment_LVAD = "Recipient Treatment: LVAD",
               `functional_status_Limited Impairment, 100-70%` = "Functional Status: Limited Impairment, 100-70%",
               `functional_status_Moderate Impairment, 50-60%` = "Functional Status: Moderate Impairment, 50-60%",
               `functional_status_Severe Impairment  40%` = "Functional Status: Limited Impairment,  40%",
               `functional_status_Unknown` = "Functional Status: Unknown",
               `wdt_time_qtile_1st quartile` = "Withdrawal-to-Death Time: 1st Quartile",
               `wdt_time_qtile_2nd quartile` = "Withdrawal-to-Death Time: 2nd Quartile",
               `wdt_time_qtile_3rd quartile` = "Withdrawal-to-Death Time: 3rd Quartile",
               `wdt_time_qtile_4th quartile` = "Withdrawal-to-Death Time: 4th Quartile",
               don_bmi = "Donor BMI"
)

love_plot_functional_status <- love.plot(post_match_nrp_dpp_fs, 
          drop.distance = TRUE, 
          stars = "raw",
          var.order = "adjusted",
          var.names = new.names,
          abs = TRUE,
          line = TRUE, 
          thresholds = c(m = .1),
          colors = c("#A33E3E", "#7CA5CB")) +
  theme_light() +
  theme(legend.position = c(.75, .3),
        legend.box.background = element_rect(), 
        legend.box.margin = margin(1, 1, 1, 1),
        axis.text.y = element_text(size = 10),
        panel.grid = element_blank())

#get matched data
matched_nrp_dpp_fs <- match.data(post_match_nrp_dpp_fs, group = "all",distance = "prop_score", data = data_nrp_dpp, drop.unmatched = TRUE)

fit_matched_dcd_fs <- survfit(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp_fs)

#matched KM
matched_with_fs <- ggsurvplot(fit_matched_dcd_fs, data = matched_nrp_dpp_fs, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", 
           ylab = "Survival Probability",
           title = "Matched Cohorts (n=204)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 
ggsave(paste0(path_save,"Supplemental Figure S4.tiff"), plot = love_plot_functional_status,height = 7,width = 14,units = "in")
ggsave(paste0(path_save, "Supplemental Figure S5.tiff"), plot = matched_with_fs, dpi = "print",width=7.29, height = 5)

```

##Add all impact factor and donor risk index terms
```{r}

data_nrp_dpp <- data_nrp_dpp %>% 
  #left_join(tx_hr %>% dplyr::select(PX_ID, CAN_DRUG_TREAT_HYPERTEN), by = "PX_ID")
  left_join(tx_hr %>% dplyr::select(PX_ID, CAN_DIAB), by = "PX_ID")
#IMPACT factor terms
  #heart failure etiology (diagnosis** all "Other")
  #hypertension (CAN_DRUG_TREAT_HYPERTEN == 1 **EMPTY!!)
  #diabetes mellitus (can_diab** EMPTY!!)
  #creatinine (can_creat)
  #serum bili (bilirubin_bins)
  #mechanical vent (rec_vent)
#donor risk index terms
  #ischemic time (total_ischemic_time)
  #donor age; (don_age)
  #race mismatching (race_mismatch)
  #blood urea nitrogen (BUN)/creatinine ratio (don_bun_creat_ratio_over_30_factor)

data_nrp_dpp1 <- data_nrp_dpp %>% 
  filter(complete.cases(
    wdt_time_qtile,
    rec_age_60 ,
    treatment ,
      don_age ,
      don_bmi ,
      CAN_MOST_RECENT_CREAT , 
      bilirubin_bins , 
      rec_vent ,
      total_ischemic_time ,
      don_age , 
      race_mismatch,
      don_bun_creat_ratio_over_30_factor
  ))

post_match_nrp_dpp_all <- matchit(nrp ~ 
                                wdt_time_qtile +
                                rec_age_60 +
                                treatment +
                                don_age +
                                don_bmi +
                                CAN_MOST_RECENT_CREAT + 
                                bilirubin_bins + 
                                rec_vent +
                                total_ischemic_time +
                                don_age + 
                                race_mismatch+
                                don_bun_creat_ratio_over_30_factor,
                   data = data_nrp_dpp1,method = "optimal",
                   distance = "glm",
                   link = "logit",
                   estimand = "ATT",
                   replace = FALSE)

new.names <- c(
               treatment_ECMO = "Recipient Treatment: ECMO",
               `treatment_High-dose Inotropes` = "Recipient Treatment: High-dose Inotropes",
               treatment_None = "Recipient Treatment: None",
               `rec_age_60_Over 60` = "Recipient Age: Over 60",
               `treatment_IABP` = "Recipient Treatment: IABP",
               treatment_Exception = "Recipient Treatment: Exception",
               `treatment_Other MCS` = "Recipient Treatment: Other MCS",
               `don_age` = "Donor Age (Years)",
               `treatment_Low-dose Inotropes` = "Recipient Treatment: Low-dose Inotropes",
               `wdt_time_qtile_1st quartile` = "Withdrawal-to-Death Time: 1st Quartile",
               `wdt_time_qtile_2nd quartile` = "Withdrawal-to-Death Time: 2nd Quartile",
               `wdt_time_qtile_3rd quartile` = "Withdrawal-to-Death Time: 3rd Quartile",
               `wdt_time_qtile_4th quartile` = "Withdrawal-to-Death Time: 4th Quartile",
               treatment_LVAD = "Recipient Treatment: LVAD",
               `don_bun_creat_ratio_over_30_factor_Over 30` = "Donor BUN:Creatinine Ratio, Greater than 30",
               `CAN_MOST_RECENT_CREAT` = "Recipient Creatinine",
              `bilirubin_bins_0-0.99` = "Recipient Bilirubin, 0-0.99",
              `bilirubin_bins_1-1.99` = "Recipient Bilirubin, 1-1.99",
              `bilirubin_bins_2-3.99` = "Recipient Bilirubin, 2-3.99",
              `bilirubin_bins_> 4` = "Recipient Bilirubin, >4",
               `don_bmi` = "Donor BMI",
               `rec_vent`="Recipient Ventilator",
              `race_mismatch_Donor/recipient race mismatch` = "Donor/Recipient Race Mismatch",
              total_ischemic_time = "Total Ischemic Time (min)")

love_plot_all<- love.plot(post_match_nrp_dpp_all, 
          drop.distance = TRUE, 
          stars = "raw",
          var.order = "adjusted",
          var.names = new.names,
          abs = TRUE,
          line = TRUE, 
          thresholds = c(m = .1),
          colors = c("#A33E3E", "#7CA5CB")) +
  theme_light() +
  theme(legend.position = c(.75, .3),
        legend.box.background = element_rect(), 
        legend.box.margin = margin(1, 1, 1, 1),
        axis.text.y = element_text(size = 10),
        panel.grid = element_blank())

#get matched data
matched_nrp_dpp_all <- match.data(post_match_nrp_dpp_all, group = "all",distance = "prop_score", data = data_nrp_dpp1, drop.unmatched = TRUE)

fit_matched_dcd_all <- survfit(Surv(surv_time_365, dead_1y) ~ nrp, data = matched_nrp_dpp_all)

#matched KM
matched_with_all <- ggsurvplot(fit_matched_dcd_all, data = matched_nrp_dpp_all, risk.table = TRUE, 
           legend.labs = c("DCD DPP", "DCD NRP"),
           legend.title = element_blank(),
           pval = TRUE,
           conf.int = TRUE,
           palette = c("#7CA5CB","#A33E3E"),
           xlab = "Days", 
           ylab = "Survival Probability",
           title = "Matched Cohorts (n=204)",
           ylim = c(0.80, 1.0),
           risk.table.fontsize = 3,  # Adjust the font size for the risk table
           break.time.by = 100,      # Set the break time for the x-axis
           xlab.text.size = 8,       # Adjust the font size for x-axis label
           ylab.text.size = 8,       # Adjust the font size for y-axis label
           legend.text.size = 8,     # Adjust the font size for legend text
           ggtheme = theme_light() +
             theme(text = element_text(size = 8),
                   axis.title.x = element_text(size = 8),
                   axis.title.y = element_text(size = 8),
                   legend.text = element_text(size = 8),
                   plot.title = element_text(size = 12),
                   axis.text.x = element_text(size = 8),
                   axis.text.y = element_text(size = 8),
                   panel.grid = element_blank()
)) 

ggsave(paste0(path_save,"Supplemental Figure S6.tiff"), plot = love_plot_all,height = 7,width = 14,units = "in")
ggsave(paste0(path_save, "Supplemental Figure S7.tiff"), plot = matched_with_all, dpi = "print",width=7.29, height = 5)

```

## Compare DBD 1-year survival by center type
```{r}
#get center IDs
dcd_ctr_ids <- data_nrp_dpp %>% 
  dplyr::select(REC_CTR_CD) %>% 
  distinct() 

nrp_ctr_ids <- data_nrp_dpp %>%
  group_by(REC_CTR_CD, nrp) %>%
  count() %>% 
  filter(nrp==1) %>% 
  dplyr::select(REC_CTR_CD) %>% 
  ungroup()

ctr_dbd_patients <- tx_list1 %>%
  filter(don_dbd =="Y") %>%
  filter(can_age > 17) %>% 
  filter(REC_CTR_CD %in% dcd_ctr_ids$REC_CTR_CD) %>%
  mutate(nrp_center = ifelse(REC_CTR_CD %in% nrp_ctr_ids$REC_CTR_CD, 1, 0)) %>% 
  mutate(
    rec_death_date = case_when(
      !is.na(PERS_SSA_DEATH_DT) ~ PERS_SSA_DEATH_DT,
      !is.na(TFL_DEATH_DT) ~ TFL_DEATH_DT)) %>% 
  mutate(dead = ifelse(!is.na(rec_death_date), 1, 0)) %>% 
  mutate(dead_1y = case_when(
    dead == 1 & (as.Date(rec_death_date) - as.Date(tx_date) < 366) ~ 1,
    dead == 0 & (as.Date(TFL_LAFUDATE) - as.Date(tx_date) < 366) ~ 0,
    dead == 0 & (as.Date(TFL_LAFUDATE) - as.Date(tx_date) >=366) ~ 0,
    dead == 1 & (as.Date(rec_death_date) - as.Date(tx_date) >=366) ~ 0
           ),
    final_dt = case_when(
          is.na(rec_death_date) == FALSE ~ rec_death_date,
          is.na(last_fu_date) == FALSE ~ last_fu_date),
    surv_time = final_dt - tx_date) %>% 
  mutate(
    surv_time_365 = ifelse(surv_time > 365 | surv_time == 365, 365, surv_time))

ctr_type_and_dbd_survival <- ctr_dbd_patients %>% 
  group_by(REC_CTR_CD, dead_1y, nrp_center) %>%
  count() %>% 
  ungroup() %>% 
  spread(key = "dead_1y", value = "n", drop = FALSE) %>% 
  rename("Living" = `0`,
         "Dead" = `1`) %>% 
  ungroup() %>% 
  mutate(Dead = ifelse(is.na(Dead), 0, Dead)) %>% 
  mutate(survival_rate_by_center = (1-Dead)*100/(Dead + Living)) %>% 
  filter(!is.na(survival_rate_by_center)) %>% 
  group_by(nrp_center) %>% 
  mutate(nrp_center_average_survival = mean(survival_rate_by_center)) %>% 
  ungroup()

center_dbd_rate <- ctr_type_and_dbd_death %>% 
  dplyr::select(REC_CTR_CD, dead_rate_by_center) %>% 
  distinct() 

dbd_survival <- ggboxplot(ctr_type_and_dbd_survival, x = "nrp_center", y = "survival_rate_by_center",
          add = "jitter",
          color = "nrp_center",
        ylab = "Survival Probability (%) at 1-Year after DBD Heart Transplantation ", 
        xlab = "Transplant Center DCD Procurement Practice") +
  scale_x_discrete(labels = c("Does Not Perform NRP", "Performs NRP")) +
  scale_color_nrp(palette = "dpp_nrp", discrete = TRUE,labels = c("Does Not Perform NRP", "Performs NRP")) +
  guides(color=guide_legend(title="Does Center Perform NRP"))

ggsave(paste0(path_save,"DBD Survival by Center.tiff"), plot= dbd_survival, height= 7, width=6, units = "in")


```



## COXME analysis without PS
```{r}
fit_coxme_unmatched1 <- coxme(Surv(surv_time_365, dead_1y) ~
                      nrp + (1|REC_CTR_CD),
                    data = data_nrp_dpp)

summary(fit_coxme_unmatched1)
```



